\chapter{System Review}
\section{System Review}

In this arena, some applications are run sequentially. Some of them are – openconf, OCS,OpenWater etc.
Some Modules of this System: Acceptance, Bidding, CAPTCHA, Form Fields, Discussion, File Type, Proceedings.\newline

\textbf{OpenConf:} Install system, check configuration and enable modules, open submission, upload and reviewer signup, assign reviewers and advocates, decision and notification.\newline

In OpenConf, there has no support to create multi-conference system,payment method,Website creation,A/R paper download option,sponsor tracking and speaker schedulingend.

\textbf{OCS(Open Conference System):} Open Conference Systems (OCS) is a free Web publishing tool that will create a complete Web presence for your scholarly conference.OCS will allow you to:create a conference Web site,compose and send a call for papers,electronically accept paper and abstract submissions,allow paper submitters to edit their work,post conference proceedings and papers in a searchable format,post,if you wish,the original data sets,register participants,integrate post-conference online discussions.\newline

In OCS, there has no support to create IEEE eCopyright,Website creation,A/R paper download option,sponsor tracking and speaker scheduling.\newline

\textbf{OpenWater:} OpenWater Conference handles everything, from abstract collection to speaker scheduling, presentation slide management, online registration collection and sponsorship tracking. No matter what you need, you know where to find it.\newline

In OCS, there has no support to create multi-conference system,IEEE eCopyright,payment method,Website creation,A/R paper download option.\newline

Above all systems,there are some advantages and disadvantages.Such as:\newline

\begin{center}
\begin{table}[htbp]
   \begin{tabular}{|c|c|c|c|}
     \hline
     % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
     Topics & OpenConf & OCS & OpenWater \\\hline
     Make Submission & Y & Y & Y \\\hline
     Allow Multiconference & N & Y & N \\\hline
     Payment System & In free addition no support & Y & N \\\hline
     Create Website  & N & N & N \\\hline
     P/N Author Registration & N & N & N \\\hline
     IEEE eCopyright & In free addition no support & N & N \\\hline
     A/R paper Download option & N & N & N \\\hline
     Program  Schedule Creation & Y & N & Y \\\hline
     Online Registration & Y & Y & Y \\\hline
     sponsorship tracking & N & N & Y \\
     Make Submission & Y & Y & Y \\\hline
     speaker scheduling & N & N & Y \\\hline
     Program management with RFID & N & N & N \\\hline


   \end{tabular}
   \caption[Pros and Cons Existing System.]{Pros and Cons Existing System}
	\label{tab:pros cons}

  \end{table}
  \end{center}


\section{Proposed  System }
Identify these problems, this proposed system target is to overcome those problems. Primarily, The Proposal entitled as IITProConf can do Peer-Review, Abstract and Conference Management. IITProConf is a free Web publishing tool that will create a complete Web presence for scholarly conference.
IITProconf covers all aspects of online conference management and publishing, from setting up conference website to operational tasks such as submitting, reviewing, editing, publishing, archiving, and indexing of the conference papers.

 IITProconf also helps to manage the people involved in organizing a conference, reviewers, and authors,notifying readers and registrants, and assisting with the correspondence. Additionally, Payment system module is added and free as open source to anyone. In existing all conference system there has no concept of RFID. Main featured of proposed system is helpful to program management with RFID technologies.\newline
Below, there is an overview of the process IITProConf uses.
\begin{center}
\begin{table}[htbp]
   \begin{tabular}{|c|c|c|c|c|c|}
     \hline
     % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
     Topics & S/A & Chair & Author & Reviewer & P/N \\\hline
     Install and Config & N & Y & N &N &N \\\hline
     Create Website & N & Y & N &N &N \\\hline
     Open and Close Submissions& Y & N & N &N &N \\\hline
     Sign-Up & N & N & Y &Y &Y \\\hline
     Decision  and Notification & N & Y & N &N &N \\\hline
     Control Conference Payment method & Y & N & N &N &N \\\hline
     Assign  Reviewers & N & Y & N & N & N \\\hline
     Open and close Reviewer Sign-In & N & Y & N & N & N \\\hline
     Review Submission & N & N & N & Y & N \\\hline
     Program management with RFID  & N & Y & N & N & N \\\hline
   \end{tabular}
   \caption[Proposed System Process.]{Proposed System Process}
	\label{tab:system process}

  \end{table}
  \end{center}






